---
title: "HW6"
author: "Jaein Shin"
date: "5/27/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning = FALSE}
# install.packages("glmnet")
# install.packages("janitor")
# install.packages("ranger")
library(tidymodels)
library(tidyverse)
library(rlang)
library(knitr)
library(discrim)
library(klaR)
library(glmnet)
library("janitor")
library(corrplot)
library(rpart.plot)
library(ranger)
library(vip)
tidymodels_prefer()
```

```{r}
setwd("/Users/james/OneDrive/Desktop/PSTAT 231/hws/jaein")
pokemon <- read_csv("Pokemon.csv")
head(pokemon)
```
# Exercise 1
```{r}
pokemon <- pokemon %>% 
  clean_names()

pokem <- pokemon %>%
  filter(type_1 %in% c("Bug", "Fire", "Grass", "Normal", "Water", "Psychic"))

pokem$type_1 <- factor(pokem$type_1)
pokem$legendary <- factor(pokem$legendary)

set.seed(101)

pokem_split <- initial_split(pokem, prop = 0.80,
                          strata = type_1)
pokem_train <- training(pokem_split)
pokem_test <- testing(pokem_split)

dim(pokem_train)
dim(pokem_test)

pokem_folds <- vfold_cv(pokem_train, v = 5, strata = type_1)
pokem_folds

pokem_recipe <- recipe(type_1 ~ legendary + generation + sp_atk + attack + speed + defense + hp + sp_def,
                    data = pokem_train) %>%
  step_dummy(c(legendary, generation)) %>%
  step_normalize(all_predictors())

head(pokemon)
```

# Exercise 2
```{r}
pokem_train %>%
  select(is.numeric) %>%
  cor() %>%
  corrplot(type = 'lower', diag = FALSE,
           method = 'color')
```

  I used all the continuous variables into account by using select(is.numeric) but I can not consider number and generation here.

 Total value has strong relation ship all the variables.

# Exercise 3

```{r}
tree_spec <- decision_tree() %>%
  set_engine("rpart")

class_tree_spec <- tree_spec %>%
  set_mode("classification")

class_tree_wf <- workflow() %>%
  add_model(class_tree_spec %>% set_args(cost_complexity = tune())) %>%
  add_recipe(pokem_recipe)

param_grid <- grid_regular(cost_complexity(range = c(-3, -1)), levels = 10)

tune_res <- tune_grid(
  class_tree_wf,
  resamples = pokem_folds,
  grid = param_grid,
  metrics = metric_set(roc_auc)
)

autoplot(tune_res)
```
1. Does a single decision tree perform better with a smaller or larger complexity penalty?
  A single decision tree perform better with a smaller complexity penalty.Since roc_auc' increases when complexity when complexity penalty decreases. 
  
# Exercise 4
```{r}
collect_metrics(tune_res)
arrange(tune_res)
best_complexity <- select_best(tune_res)
best_complexity
```

  My best-performing pruned decision tree on the folds is 0.679.
  
# Exercise 5
```{r}
class_tree_final <- finalize_workflow(class_tree_wf, best_complexity)

class_tree_final_fit <- fit(class_tree_final, data = pokem_train)

class_tree_final_fit %>%
  extract_fit_engine() %>%
  rpart.plot()
```
# Exercise 5
```{r}
class_forest_spec <- rand_forest() %>%
  set_engine("ranger", importance = "impurity") %>%
  set_mode("classification")

param_grid2 <- grid_regular(mtry(range = c(1, 8)), trees(range = c(1,8)), min_n(range = c(1,8)),  levels = 8)

forest_workflow <- workflow() %>%
  add_model(class_forest_spec %>% set_args(mtry = tune(), trees = tune(), min_n = tune())) %>%
  add_recipe(pokem_recipe)
```
1. mtry shouldn't be smaller than 1 or larger than 8. Explain why not
  mtry should fall between 1 and 8 because there are 8 variables, hence, the maximum for mtry is 8.
2. What type of model would mtry=8 represent?
  mtry=8 represents the creation of decision tree It should not be smaller than 1 or larger than 8 because the value does not show up correctly
  
# Exercise 6
```{r}
tune_res_forest <- tune_grid(
  forest_workflow,
  resamples = pokem_folds,
  grid = param_grid2,
  metrics = metric_set(roc_auc)
)

autoplot(tune_res_forest)
```


# Exercise 7
```{r}
collect_metrics(tune_res_forest)
arrange(tune_res_forest)
best_complexity2 <- select_best(tune_res_forest)
best_complexity2
```



# Exercise 8
```{r}
class_tree_final_fit %>%
  pull_workflow_fit() %>%
  vip()
```



# Exercise 9 
```{r}
boost_spec <- boost_tree(trees = c(10,2000), tree_depth = 4) %>%
  set_engine("xgboost") %>%
  set_mode("classification")

param_grid_boost <- grid_regular(trees(range = c(10, 2000)),  levels = 10)

boost_workflow <- workflow() %>%
  add_model(boost_spec %>% set_args(trees = tune())) %>%
  add_recipe(pokem_recipe)

tune_res_boost <- tune_grid(
  boost_workflow,
  resamples = pokem_folds,
  grid = param_grid_boost,
  metrics = metric_set(roc_auc)
)

autoplot(tune_res_boost)

collect_metrics(tune_res_boost)
arrange(tune_res_boost)
best_complexity3 <- select_best(tune_res_boost)
best_complexity3
```

  the roc_auc of my best-performing boosted tree model on the folds is 0.721.
  
# Exercise 10
```{r}
pokem <- data.frame(best_performing = c(0.6683123, 0.7219142, 0.6944132),
                 models <- c("pruned tree model", "random forest model", "boosted tree model"))

head(pokem)

#fit it to the testing set
best_complexity <- select_best(tune_res)

class_tree_final <- finalize_workflow(forest_workflow, best_complexity2)

class_tree_final_fit <- fit(class_tree_final, data = pokem_test)

pred_result <- augment(class_tree_final_fit, new_data = pokem_test)
auc <- roc_auc(data = pred_result, truth = type_1, estimate = c(.pred_Bug, .pred_Fire, .pred_Grass, .pred_Normal, .pred_Water, .pred_Psychic ), estimator = "macro_weighted")
auc

augment(class_tree_final_fit, new_data = pokem_test) %>%
  roc_curve(type_1, estimate = .pred_Bug, .pred_Fire, .pred_Grass, .pred_Normal, .pred_Water, .pred_Psychic) %>%
  autoplot()

augment(class_tree_final_fit, new_data = pokem_test) %>%
  conf_mat(truth = type_1, estimate = .pred_class) %>%
  autoplot(type = "heatmap")

pred_result <- augment(class_tree_final_fit, new_data = pokem_test)
auc <- roc_auc(data = pred_result, truth = type_1, estimate = c(.pred_Bug, .pred_Fire, .pred_Grass, .pred_Normal, .pred_Water, .pred_Psychic ), estimator = "macro_weighted")
auc

```

